|

### 2023-05-09 paper/01-introduction.Rmd
figure size, literature

The literature on the performance of linemen, either offensive or defensive in football is scant.
@AlamarGould2008 examine the the relationship between pass completion and offensive linemen's performance, in terms of how successful they were at blocking.
The data for this study are manually collected for the first three weeks of the 2007 NFL season, recording whether a lineman holds a block and the time in pocket for the quarterback.

Later, @AlamarGoldner2011 use manually-tracked data during the 2010 season to estimate lineman performance for different team-positions instead of individual defenders (e.g. Chicago Bears' left tackle, Pittsburgh Steelers' center).
[this next part needs re-wording]
They then go on to use a survival analysis model to estimate time in pocket.  The average probability of success from the survival model is then used as a covariate in a model to estimate the probability of competing a pass, and they show that there is a significant relationship between these two probabilities.

>>>>

The literature on the performance of linemen, either offensive or defensive in football is scant.
@AlamarGould2008 find an association between pass completion rate and successful pass blocking by offensive linemen.
The data for this study are collected for the first three weeks of the 2007 NFL season, manually recording whether a lineman holds a block and the time it took for quarterback to throw the football.
Later, @AlamarGoldner2011 use manually-tracked data during the 2010 season to estimate lineman performance for different team-positions instead of individual defenders (e.g. Chicago Bears' left tackle, Pittsburgh Steelers' center).
The paper uses survival analysis to model time in pocket and completion percentage for quarterbacks, before ultimately measures a lineman's contribution to the overall offense in terms of yards gained.

<!-- [this next part needs re-wording] -->
<!-- They then go on to use a survival analysis model to estimate time in pocket.  The average probability of success from the survival model is then used as a covariate in a model to estimate the probability of competing a pass, and they show that there is a significant relationship between these two probabilities. -->
